---
title: "Lab 7"
output: word_document
---

Dependencies

```{r}
#R depndencies

library(dplyr)
library(plyr)
library(factoextra)
library(reticulate)
library(funModeling)
library(scatterplot3d)
library(hrbrthemes)
library(GGally)
library(viridis)
library(ggplot2)
```

```{r}
#Python dependencies

sns <- import('seaborn')
plt <- import('matplotlib.pyplot')
pd <- import('pandas')
```


```{r}
#Homemade
equal.freq.n<-function(nb,n){
  nb<-equal_freq(nb,n)
  nb<-as.numeric(factor(nb,levels=unique(nb)))
  return (nb)
}

```


Load Data:

```{r}

setwd('C:/Users/SASWATA/Desktop/Study ebooks/Sem 6/CSE4029/LAB')
dset<-read.csv('Lab10_data.csv')
set.seed(96)
```

Boxplots:

```{r}
boxplot(dset[dset$Gender=='Female',5],main="Female")
boxplot(dset[dset$Gender=='Male',5],main="Male")
```

From boxplot we observe that male spending score is more variable and thus the cluster should be more spread out in 'Gender' axis.
Also a larger number of points lie in the 1st qualtile to median range.

```{r}
boxplot(dset[dset$Gender=='Female',4],main="Female")
boxplot(dset[dset$Gender=='Male',4],main="Male")
```

We notice the opposite trend for Annual Income. The male population has greater outliers, while the femalepopulation has more values tending to the extremities.


```{r}
sns$pairplot(r_to_py(dset[,-1]),hue='Gender',palette=c('green','red'))
plt$show()
```

From the pair plot:
1> Gender doesn't affect the distribution with respect to other variables, so we will drop.
2> The Distributions are mildly skewed but the feature space will be disturbed if we treat them. So we will ignore.
3> Clearly there is class imbalance,but kmeans is not effected by imbalance, so we will not resample the data either.
4> Normalizing the data will disproportionately change the euclidean distances between observations, so we will not normalize.


```{r}
gend<-dset[,2]
dset<-dset[,-c(1,2)]
names(dset)
names(dset)[2]<-'AI'
names(dset)[3]<-'SS'
```

```{r}
ageai<-dset[,c(1,2)]
agess<-dset[,c(1,3)]
ssai<-dset[,c(2,3)]
```


```{r}
fviz_nbclust(ageai, kmeans, method = "silhouette")
fviz_nbclust(agess, kmeans, method = "silhouette")
fviz_nbclust(ssai, kmeans, method = "silhouette")
fviz_nbclust(dset, kmeans, method = "silhouette")
```

```{r}
km.12 <- kmeans(ageai, 2, nstart = 25)
print(km.12)
km.13 <- kmeans(agess, 4, nstart = 25)
print(km.13)
km.23 <- kmeans(ssai, 6, nstart = 25)
print(km.23)
km.123 <- kmeans(dset, 6, nstart = 25)
print(km.123)
```

```{r}
fviz_cluster(km.12, data = ageai,
             palette = c("#2E9FDF", "#00AFBB"),#, "#E7B800", "#FC4E07"),
             ellipse.type = "euclid", # Concentration ellipse
             star.plot = TRUE, # Add segments from centroids to items
             repel = TRUE, # Avoid label overplotting (slow)
             ggtheme = theme_minimal()
)
fviz_cluster(km.13, data = agess,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07"),
             ellipse.type = "euclid", # Concentration ellipse
             star.plot = TRUE, # Add segments from centroids to items
             repel = TRUE, # Avoid label overplotting (slow)
             ggtheme = theme_minimal()
)
fviz_cluster(km.23, data = ssai,
             palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07","#5AA897","#DE8971"),
             ellipse.type = "euclid", # Concentration ellipse
             star.plot = TRUE, # Add segments from centroids to items
             repel = TRUE, # Avoid label overplotting (slow)
             ggtheme = theme_minimal()
)
fviz_cluster(km.123, data = dset,
             palette = c("#DE8971", "#00AFBB", "#E7B800", "#FC4E07","#23049D","#5AA897"),
             ellipse.type = "euclid", # Concentration ellipse
             star.plot = TRUE, # Add segments from centroids to items
             repel = TRUE, # Avoid label overplotting (slow)
             ggtheme = theme_minimal()
)
```

```{r}
scatterplot3d(dset[,1:3], pch=20, color=rainbow(6)[km.123$cluster])
```

We will probe into the best clustering 'km.23' acc(86.2) and try to understand it.

```{r}
nv<-as.numeric(unlist(km.23[1]))
dset.23<-cbind(dset,data.frame(cluster=as.factor(nv)))
str(dset.23)
```


```{r}
dset.gend<-cbind(dset.23,data.frame(Gender=as.factor(gend)))
str(dset.gend)
```

```{r}
#Coordinate Parallel Plot wrt Variables
ggparcoord(dset.23,
    columns = 1:4, groupColumn = 4,
    showPoints = TRUE,
    alphaLines = 0.3
    ) + 
  scale_color_viridis(discrete=TRUE) +
  theme_ipsum()+
  theme(
    plot.title = element_text(size=10)
  )

```


```{r}
#Coordinate Parallel Plot wrt Gender
ggparcoord(dset.gend,
    columns = 1:4, groupColumn = 5,
    showPoints = TRUE,
    alphaLines = 0.3,
    ) + 
  scale_color_viridis(discrete=TRUE) +
  theme_ipsum()+
  theme(
    plot.title = element_text(size=10)
  )
```




Conclusion:

We see that the clustering is most well define when clustered with 'Annual Income' and 'Spending Score'. Adding the 'Age' of the customer to the mix only reduces the accuracy of the clusters meaning it is noise and not useful for clustering. It can however help visualize the spread of the data points in each cluster.
In the optimal condition we have found 6 clusters. Using the Parallel Coordinate Plot, we will try to interpret these clusters and further understand the consequence of clustering.

Clusters:

1> Cluster1 (purple): Older customers representing the lower ends of Annual Income and Spending score both above and below the medians.
2> Cluster2 (dark blue): Average age and Annual Income but low Spending Score.
3> Cluster3 (blue): Younger in age and representing both Annual Income and Spending Score between 1st quantile and Median.
4> Cluster4 (deep green): Younger in age and representing high Spending Score and average Annual Income.
5> Cluster5 (green): Youngest in Age, Highest in both Annual income and Spending Score.
6> Cluster6 (yellow): Age tending towards the 1st quartile, Annual Income lying between the median and 3rd quaartile touching the median, Spending Score also in the same range, touching the 3rd Quartile.

There can be multiple uses for this data like developing infrastructure, re stocking, etc, but we will focus on marketing effort per cluster.

Clusters 1,2 and 3 have either older customers who are less likely to be swept by offers and lower income and spending power. This bakes them a bad target for marketing effort because there is not much value to be extracted.
Cluster 4 also represents customers who have comparatively high spending power and income but are consistent in their display of interest wit respect to their capacity.

Cluster 6 and 5 are the best targets for marketing as their incomes are very high and so is their tendency to spend. Youngsters are also more likely to be swayed by marketing. They display a clear interest in spending, so more value can be extracted. Considering the fact that the 2 clusters have relatively separable Incomes, but spend more or 
less the same, there is room to push the spending score, specially for cluster 6.